Supplemental material for: Timing and magnitude of climate driven range shifts in transboundary fish stocks challenge their management

### 2021-12-01 Scripts/Supplements.Rmd
Created equation table

>>>>

```{r}
library(tidyverse)
library(knitr)

data.frame(
   "Acronym" = c(
     "Hs",
     "_i_",
     "_T_",
     "TPP",
     "B$\\alpha$~i~",
     "Min~D~",
     "Max~D~",
     "Hab~ij~",
     "_u_",
     "Hab~Assoc~",
     "Sal",
     "Sal~Assoc~",
     "Ice",
     "Ice~p~",
     "A~i~",
     "_G_",
     "L~ji~",
     "Ad~ji~",
     "_j_",
     "_r_",
     "_K_",
     "_f_",
     "lat~ts~",
     "lat~per~",
     "lon~ts~",
     "lon~per~",
     "$\\mu$",
     "per^th^",
     "D~ens~",
     "lat~EEZ~",
     "lat~ts~",
     "lon~EEZ~",
     "lon~ts~",
     "TSI",
     "D~A~",
     "D~B~",
     "sd",
     "t",
     "th",
     "ToE",
     "TSI~$\\mu$~",
     "TSI~f$\\mu$~",
     "TSI~$\\omega$~",
     "_t'_",
     "tresh",
     "ToE",
     "SSR~th~",
     "SSR~te~",
     "SSR~tm~",
     "SSR~tf~",
     "_s_"

     ),
   "Meaning" = c(
     "Habitat suitability",
     "Grid-cell of 0.5^o^ latitude x 0.5^p^ longitude",
     "Seawater temperature",
     "Species temperature profile",
     "Bathymetry",
     "Species' minimum depth limit",
     "Species' maximum depth limit",
     "Proportion of area of the habitat type",
     "Habitat type",
     "Habitat association index",
     "Salinity",
     "Salinity association index",
     "Sea ice extent",
     "Association to sea ice",
     "Relative abundance of a given species in each grid-cell _i_",
     "Intrinsic population growth",
     "Number of settled larvae",
     "Net migrated adults from surrounding cells _j_",
     "Surrounding grid-cell",
     "Intrinsic rate of population increase",
     "Carrying capacity of grid-cell _i_",
     "Fishing mortality",
     "Average latitude across the high-abundance grid-cells",
     "Latitude of grid-cells holding a given percentile of projected abundance",
     "Average longitude across the high-abundance grid-cells",
     "Longitude of grid-cells holding a given percentile of projected abundance",
     "Mean",
     "Percentile of projected transboundary stock abundance",
     "Distance between the centroid of the EEZs and the centroid of the transboundary stock",
     "Latitude of the EEZ's centroid",
     "Latitude of the transboundary stock's centroid",
     "Longitude of the EEZ's centroid",
     "Longitude of the transboundary stock's centroid",
     "Transboundary Stock Index",
     "Distance between the distribution centroids of a stock and the centroid of the neighboring EEZs A",
     "Distance between the distribution centroids of a stock and the centroid of the neighboring EEZs B",
     "Standard deviation",
     "Time step from 1951 to 2006",
     "Historical time period (1951 to 2005)",
     "Time of emergence",
     "Average TSI from 1951 to 2005",
     "Average TSI from 2006 to 2100",
     "Standard deviation of TSI from 1951 to 2005",
     "Years from 2006 to 2100",
     "Threshold to determine the time of emergence",
     "Year when TSI~f$\\mu$~ overpasses the _tresh_",
     "Stocks share ratio over the historical time period (1951 to 2005)",
     "Stocks share ratio at the early time period (2020 to 2040)",
     "Stocks share ratio at the late time period (2050 to 2060)",
     "Stocks share ratio at the early or late time period",
     "Stock whose share ratio exceeded the threat point of an EEZ"
   )
) %>% 
  kable()
```
